Results

### 2024-10-02 scripts/Results.Rmd
reworked leaf plot

  geom_label(data = labs, aes(x = x, y = y, label = label), 
             inherit.aes = F, size = 2.5 ,

@@

rm(fp, fp_2, fp_5, fp_8, labs, prctn, sm50, sm80, linecols)
```

>>>>

  geom_label(data = labs, aes(x = x, y = y, label = label), 
             inherit.aes = F, size = 3 ,

@@

# rm(fp, fp_2, fp_5, fp_8, labs, prctn, sm50, sm80, linecols)
```
